---
title: "Data on air pollution registered in Czech Republic in the period from 2013 to 2019"
output: word_document
params:
  AirPollutant: NA
  Aggregation: NA
  X_axis: NA
  selected_stations: NA
  thresholds: NA
  plot: NA
  stationmap: NA
  table: NA
  

---
# Registration of `r params$AirPollutant` has been performed on the stations below:

```{r include=FALSE}
library(knitr)
library(webshot)
```


```{r echo=FALSE, results='asis'}
cat(paste('*', params$selected_stations), sep = '\n')
```

# Stations are located here
```{r echo=FALSE, fig.height=7.5, fig.width=7.5}
#Plotting the map works pretty well on local servier, however it does not when deployed on Server.
#I tried several ways to solve it but with no result.
params$stationmap
```


# Chart of concentration of `r params$AirPollutant` in the atmosphere.

## Parameters of the chart:

* Level of aggregation: `r params$Aggregation`
* Type of presentation of time axis: `r params$X_axis`

```{r echo=FALSE, fig.width=9, warning=FALSE}
params$plot
```


### Concentrations of the pollutant (yearly/daily/hourly averages where applicable) that are considered safe in accordance with EU air quality standards (mu*g/m^3^):

```{r echo=FALSE}
tb <- params$thresholds %>% 
  dplyr::filter(AirPollutant == params$AirPollutant)
knitr::kable(tb)

```


# Below are the first 5 rows of the table with concentration data. Full table can be downloaded from ShinyApp in CSV format.

```{r echo=FALSE}
knitr::kable(head(params$table))
```



